---
title: "plot"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{plot}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

The 'OEI' package was developed as a way of quickly accessing data from databases maintained by the Ocean Ecology group.

```{r setup}
library(OEI)
```

This is a plot of the table data with no categories
```{r, include = TRUE}

#pretend this is a data.frame from the db

#myDataFrame <- getTable()


myDataFrame <- data.frame(y = rnorm(100) 
                          ,x = sample(1998:2021,100,replace=TRUE)
                          #,Index = sample(c("SST","NPI","PTSD"), 100, replace=TRUE)
                          )
OEI::oeiplot(myDataFrame)

```

This is a plot of the table data with categories. Same function call different data.frame, different plot.
```{r, include = TRUE}

#pretend this is a data.frame from the db

#myDataFrame <- getTable()


myDataFrame <- data.frame(y = rnorm(100) 
                          ,x = sample(1998:2021,100,replace=TRUE)
                          ,Index = sample(c("SST","NPI","PTSD"), 100, replace=TRUE)
                          )
OEI::oeiplot(myDataFrame)

```


This is a plot of the table data with categories. Same function call different data.frame, different plot.
```{r, include = TRUE}

#pretend this is a data.frame from the db

#myDataFrame <- getTable()


myDataFrame <- data.frame(y = rnorm(100) 
                          ,x = sample(1998:2021,100,replace=TRUE)
                          ,Index = sample(c("SST","NPI","PTSD"), 100, replace=TRUE)
                          )
OEI::oeiplot(myDataFrame, multipane = TRUE)

```
